---
output: pdf_document
geometry: margin=0.5in
params:
  version: 'NULL'
  anc_count: 'NULL'
  anc_prev: 'NULL'
  anc_known: 'NULL'
  anc_art: 'NULL'
  threshold: 'NULL'
  title: 'NULL'
title: "`r params$title`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These plots have been generated to assist in validating input data for Naomi by ShinyRob.

The data were extracted from the AIDS Data Repository, and last modified at: `r params$version`

For plots of numbers of ANC clients, period-on-period changes greater than `r params$threshold`% are highlighted in red.



# Numbers of ANC clients

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
for (i in 1:length(params$anc_count)) {
  print(params$anc_count[[i]])
  # print(foo[[i]])
   cat("\n\n\\pagebreak\n")
 }
```

# HIV prevalence among ANC attendees 

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
for (i in 1:length(params$anc_count)) {
  print(params$anc_prev[[i]])
  cat("\n\n\\pagebreak\n")
}
```

# Percentage of known positive already on ART 

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
for (i in 1:length(params$anc_count)) {
  print(params$anc_known[[i]])
   cat("\n\n\\pagebreak\n")
 }
```

# ART coverage prior to first ANC visit

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
for (i in 1:length(params$anc_count)) {
  print(params$anc_art[[i]])
   cat("\n\n\\pagebreak\n")
 }
```