---
output: pdf_document
geometry: margin=0.5in
params:
  version: 'NULL'
  art_count: 'NULL'
  art_sex_ratio: 'NULL'
  art_sex_flag: 'NULL'
  art_paediatric: 'NULL'
  threshold: 'NULL'
  title: 'NULL'
title: "`r params$title`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These plots have been generated to assist in validating input data for Naomi by ShinyRob.

The data were extracted from the AIDS Data Repository, and last modified at: `r params$version`

For plots of numbers on ART, period-on-period changes greater than `r params$threshold`% are highlighted in red.



# Numbers on ART

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
for (i in 1:length(params$art_count)) {
  print(params$art_count[[i]])
  # print(foo[[i]])
   cat("\n\n\\pagebreak\n")
 }
```

# Female-to-male sex ratio among adults on ART

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
if(params$art_sex_flag) {
  for (i in 1:length(params$art_count)) {
    print(params$art_sex_ratio[[i]])
     cat("\n\n\\pagebreak\n")
  }
} else {
  print("No sex disaggregated ART data available")
}
```

# Proportion of total on-ART under age 15

```{r, echo=FALSE, results='asis', warning = FALSE, message = FALSE, fig.height=12, fig.width=9}
for (i in 1:length(params$art_count)) {
  print(params$art_paediatric[[i]])
   cat("\n\n\\pagebreak\n")
 }
```
